### 2014-10-08 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Minor edits to Section 3

Smokeview is a software tool designed to visualize simulation results from FDS~\cite{Smokeview_Users_Guide}. Smokeview visualizes smoke and other attributes of the fire simulation using traditional scientific methods such as displaying tracer particle flow, two dimensional (2D) or three dimensional (3D) shaded contours of gas flow data such as temperature and flow vectors showing flow direction and magnitude. Smokeview has the ability to visualize fire and smoke by displaying a series of partially transparent planes where the transparencies in each plane (at each grid node) are determined from soot densities computed by FDS. Smokeview can also visualize data at particular snapshots in time using 2D or 3D contours of data such as temperature and flow vectors showing flow direction and magnitude.

Input data from various sources must be collected and documented to simulate a fire using FDS or any other fire model. For the simulation results presented in this document, information was obtained from two primary sources. The following information was gathered from the fire scene: the geometry of the building and the compartments being modeled, the size and location of exterior and interior ventilation openings, and documentation of fire damage to the building. The following information was gathered from witnesses, first responders, reports, and recorded media such as fire ground radios or photographs: information on the timing of the fire development, the sequence and approximate timing of ventilation openings to the outside, and weather conditions at the time of the fire.

@@

The structure involved in this fire incident was a four-story residential building with a flat roof that consisted of a bitumen membrane. The exterior was primarily stucco with large windows on the top three stories of the rear side of the structure. The structure had exterior dimensions of 8.53~m (28~ft) by 17.73~m (58~ft) and a height of 5.9~m (19~ft), as shown in Fig.~\ref{fig:floor_plan}. The right side of the structure shared a common fire wall with another residential structure.

@@

The basement (i.e., the first story below street level) had a total floor area of 121~m$^2$ (1301~ft$^2$) and consisted of a finished living area with a large utility area. A laundry area was located on a landing on the stairs between the first floor and basement. The basement was accessible via this interior set of stairs or via an exterior door on the left side of the structure. The basement had an exterior balcony on the rear side of the structure. The sub-basement level (i.e., the second story below street level) was not connected to the other three levels of the house, contained no windows, and was only accessible via an exterior door of the left side of the structure. The exterior entrances to the basement and sub-basement levels were connected via exterior wooden stairs on the left side of the structure.

@@

As discussed in Section~\ref{sec:geometry}, the structure had exterior dimensions of 8.53~m (28~ft) by 17.73~m (58~ft) and a total height of 5.9~m (19~ft). To ensure adequately resolved fluid flow in and out of the structure, the computational domain was extended beyond the volume of the structure. The dimensions of the computational domain were 11.5~m (38~ft) by 22~m (72~ft) and a height of 13.6~m (45~ft). A grid resolution of 10~cm (3.9~in) was used, which resulted in a total of approximately 3.4 million computational cells. As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas snapped to the nearest 10~cm. Figure~\ref{fig:SMV_exterior_grid} shows the front and rear sides of the structure rendered in Smokeview with the 10~cm mesh.

>>>>

Smokeview is a software tool designed to visualize simulation results from FDS~\cite{Smokeview_Users_Guide}. Smokeview visualizes smoke and other attributes of the fire simulation using traditional scientific methods such as displaying tracer particle flow, two dimensional (2D) or three dimensional (3D) shaded contours of gas flow data such as temperature and flow vectors showing flow direction and magnitude. Smokeview has the ability to visualize fire and smoke by displaying a series of partially transparent planes where the transparencies in each plane (at each grid node) are determined from soot densities computed by FDS. Smokeview can also visualize data at particular snapshots in time using 2D or 3D contours of data that show temperature, flow direction, and flow magnitude.

Input data from various sources must be collected and documented to simulate a fire using FDS or any other fire model. For the simulation results presented in this document, information was obtained from two primary sources. The following information was gathered from the fire scene: the geometry of the building and the compartments being modeled, the size and location of exterior and interior ventilation openings, and documentation of fire damage to the building. The following information was gathered from witnesses, first responders, reports, and recorded media such as fire ground radios or photographs: information on the fire development timeline, the sequence and approximate timing of ventilation openings to the outside, and weather conditions.

@@

The structure involved in this fire incident was a four-story residential building with a flat roof that consisted of a bitumen membrane. The exterior was primarily stucco with large windows on the top three stories of the rear side of the structure. The structure had exterior dimensions of 8.53~m (28~ft) by 17.73~m (58~ft) and a height of 5.9~m (19~ft) above street level, as shown in Fig.~\ref{fig:floor_plan}. The right side of the structure shared a common fire wall with another residential structure.

@@

The basement (i.e., the first story below street level) had a total floor area of 121~m$^2$ (1301~ft$^2$) and consisted of a finished living area and a large utility area. A laundry area was located on a landing on the interior stairwell between the first floor and basement. The basement was accessible via this interior set of stairs or via an exterior door on the left side of the structure. The basement had an exterior balcony on the rear side of the structure. The sub-basement level (i.e., the second story below street level) was not connected to the other three levels of the house, contained no windows, and was only accessible via an exterior door of the left side of the structure. The exterior entrances to the basement and sub-basement levels were connected via exterior wooden stairs on the left side of the structure.

@@

As discussed in Section~\ref{sec:geometry}, the structure had exterior dimensions of 8.53~m (28~ft) by 17.73~m (58~ft) and a height of 5.9~m (19~ft) above street level. To ensure adequately resolved fluid flow in and out of the structure, the computational domain was extended beyond the volume of the structure. The dimensions of the computational domain were 11.5~m (38~ft) by 22~m (72~ft) and a height of 13.6~m (45~ft). A grid resolution of 10~cm (3.9~in) was used, which resulted in a total of approximately 3.4 million computational cells. As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas snapped to the nearest 10~cm. Figure~\ref{fig:SMV_exterior_grid} shows the front and rear sides of the structure rendered in Smokeview with the 10~cm mesh.
